Mathematical Language Processing \\ Project

### 2014-02-26 paper.tex
Little corrections of the abstract

\begin{abstract}
In this paper, we present a solution for automated definition discovery for the variables occurring in mathematical formulae.
Ordinary natural language processing approaches that are trained based on large manually annotated news corpora fall short in reasonable quality of definition discovery for scientific texts.
In the \emph{Mathematical Language Processing} project we discover definition relations between variables and the surrounding text with a machine learning approach for classification. We extract the identifiers from the formulae and track co-occurrences of those in the surrounding text.
The evaluation of our prototypical system, applied on the Wikipedia text corpus shows, that our approach augments the user experience for articles with mathematical formula substantially. While hovering the identifiers occurring in the equation a pop-up with the most probable explanations for the identifiers occurs. The displayed definition information provides a good match to the actual meaning of the identifiers.
\keywords{machine learning, text mining, parallel computing}
\end{abstract}

@@

Unfortunately, no one has built a labelled text corpus that annotates variables and their definition. Instead of labelling large amounts of text by hand, we investigate a potential way of automatically labelling large corpora with a set of statistical assumptions.

We chose the Wikipedia text corpus as a target because of two facts. First, the mark-up for editing formulas is a subset of \TeX. Therefore, it enables us to collect all variables within the set of formulas in a document. Second, we can leverage the semantic information between mark-up and word tokens, e.g., hyperlinks.

@@

Thereby we performed the normalisation, with regard to the model assumption that the probability to find a relation at $\Delta=1$ is maximal, i.e. $R(1)=1$. 
Manual evaluation of some articles indicated that $R(1)\approx\frac{1}{2}R(5)$.
As, the full width half maximum is at $\Delta=\sqrt{2 \ln(2)  \sigma^2+1}$, and the standard deviation evaluates to $\sigma(\Delta)=\sqrt\frac{\Delta^2-1}{2\ln 2}$. As a consequence we choose $\sigma_d=\sqrt\frac{5^2-1}{2\ln 2}$ and write $R_\mathrm{d}(\Delta) \equiv R_{\sigma_\mathrm{d}}(\Delta) $. Please note that this assumption is heavily influenced by the language of the text corpus.

Not only the distances within one sentence are of interest. Also the sequential order of sentences, containing a variable, carry some viable sources for statistics. Typically an author first introduces a term and uses it in subsequent sentences without necessarily repeating its definition. We assume that this kind of behaviour also applies to the use of variables. Thus, we extend the idea of distance to the sequential order of sentences. Here, the distance is the count $n$ of candidate sentences, beginning at the top of the document.

@@

>>>>

\begin{abstract}
In this paper, we present a solution for automated definition discovery for the variables occurring in mathematical formulae.
Ordinary natural language processing approaches that are trained based on large, manually annotated news corpora fall short in reasonable quality of definition discovery for scientific texts.
In the \emph{Mathematical Language Processing} project, we discover definitions %we did not discover any relations
% a relation would be something like "let <subj> be a <object>", or "we call <subj> <obj>", or "<subject> is <object>" or just "<subj> <obj>"
 for identifiers in formulae from the surrounding text by statistical methods.
 %with a machine learning approach for classification. This was also not done in this paper
%We extract the identifiers from the formulae and track co-occurrences of those in the surrounding text.
The evaluation of our prototypical system, applied on the Wikipedia text corpus shows that our approach augments the user experience for articles with mathematical formula substantially.
While hovering the identifiers occurring in the equation a pop-up with the most probable explanations for the identifiers occurs. The displayed definition information provides a good match to the actual meaning of the identifiers.
\keywords{machine learning, text mining, parallel computing}
\end{abstract}

@@

Unfortunately, no one has built a labeled text corpus that annotates variables and their definition. Instead of labeling large amounts of text by hand, we investigate a potential way of automatically labeling large corpora with a set of statistical assumptions.

We chose the Wikipedia text corpus as a target because of two facts. First, the mark-up for editing formulas is essentially a subset of \TeX. Therefore, it enables us to collect all variables within the set of formulas in a document. Second, we can leverage the semantic information between mark-up and word tokens, e.g., hyperlinks.

@@

Thereby we performed the normalization, with regard to the model assumption that the probability to find a relation at $\Delta=1$ is maximal, i.e. $R(1)=1$. 
Manual evaluation of some articles indicated that $R(1)\approx\frac{1}{2}R(5)$.
As, the full width half maximum is at $\Delta=\sqrt{2 \ln(2)  \sigma^2+1}$, and the standard deviation evaluates to $\sigma(\Delta)=\sqrt\frac{\Delta^2-1}{2\ln 2}$. As a consequence we choose $\sigma_d=\sqrt\frac{5^2-1}{2\ln 2}$ and write $R_\mathrm{d}(\Delta) \equiv R_{\sigma_\mathrm{d}}(\Delta) $. Please note that this assumption is heavily influenced by the language of the text corpus.

Not only the distances within one sentence are of interest. Also the sequential order of sentences, containing a variable, carry some viable sources for statistics. Typically an author first introduces a term and uses it in subsequent sentences without necessarily repeating its definition. We assume that this kind of behavior also applies to the use of variables. Thus, we extend the idea of distance to the sequential order of sentences. Here, the distance is the count $n$ of candidate sentences, beginning at the top of the document.

@@

%460 identifiers
